Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-03-13 docs/thesis/appendix-conf_files.tex
Work on thesis doc: Added intro section and status of MIR.
added clustering section

\chapter{Configuration files}

\section{Solr Schema}
The Solr schema file \verb|schema.xml| indicates which are the fields that are going to be used in this instance, and what type of analyzer is going to be used for each one. One can also define field types in case different fields want to have the same behaviour but conceptually having different meanings.

>>>>

\chapter{Configuration files}
\label{appendix-conf_files}

\section{Solr schema}
The Solr schema file \verb|schema.xml| indicates which are the fields that are going to be used in this instance, and what type of analyzer is going to be used for each one. One can also define field types in case different fields want to have the same behaviour but conceptually having different meanings.

### 2014-03-13 docs/thesis/chap-clustering.tex
added clustering section

We used Apache Mahout v0.9 for performing the clustering task. 
The following set of commands were used to create and analyse our dataset:

@@

\small{{\codefont ./mahout lucene.vector -d <path to solr index>  -o ../results/vectors -t ../results/dict -f math           \_notational\_field -st ../results/dict\_seq -x 20 -md 2 -w TFIDF -n 2}}

@@

The resulting clusters can help us to identify common structures and further improve our results by either adding frequent structures that are common to a cluster, or by reducing the number of elements to perform comparisons against and allow to speed-up the querying process.
Table \ref{} shows the top terms in 2 different clusters that were identified. By simple inspection, it is possible to identify the first one as a cluster grouping trigonometric expressions (Sines and Cosines) and the second one grouping limits where the variable goes to infinity.

@@

\caption{Top 20 terms for two different identified clusters }
\label{cluster_measurements}
\end{longtable} 
}

>>>>

We used Apache Mahout v0.9\cite{mahout} for performing the clustering task. 
The following set of commands were used to create and analyse our dataset:

@@

\small{{\codefont ./mahout lucene.vector -d <path to solr index>  -o ../results/vectors -t ../results/dict -f math\_notational\_field -st ../results/dict\_seq -x 20 -md 2 -w TFIDF -n 2}}

@@

The resulting clusters can help us to identify common structures and further improve our results by either adding frequent structures that are common to a cluster, or by reducing the number of elements to perform comparisons against and allow to speed-up the querying process.
Table \ref{top_terms} shows the top terms in 2 different clusters that were identified. By simple inspection, it is possible to identify the first one as a cluster grouping trigonometric expressions (Sines and Cosines) and the second one grouping limits where the variable goes to infinity.

@@

\caption{Top 20 terms for two different identified clusters }
\label{top_terms}
\end{longtable} 
}
